---
title: "UBSN ROI Follow-up Inference"
output:
  html_document:
    toc: true
    toc_depth: 2
    df_print: paged
---

```{r setup, message=FALSE, warning=FALSE}
required_packages <- c(
  "tidyverse",
  "lme4",
  "lmerTest",
  "emmeans",
  "broom",
  "broom.mixed",
  "openxlsx",
  "patchwork",
  "scales"
)

missing_packages <- required_packages[!vapply(required_packages, requireNamespace, logical(1), quietly = TRUE)]
if (length(missing_packages) > 0) {
  stop(
    "Please install these R packages before running this Rmd: ",
    paste(missing_packages, collapse = ", ")
  )
}

library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(broom)
library(broom.mixed)
library(openxlsx)
library(patchwork)
library(scales)

theme_set(theme_bw(base_size = 13))

project_dir <- "CHANGE_THIS_TO_YOUR_PROJECT_DIR"
base_dir <- file.path(project_dir, "UBSN_abstract_outputs", "tables")
output_root <- file.path(project_dir, "UBSN_followup_inference_outputs")
table_dir <- file.path(output_root, "tables")
figure_dir <- file.path(output_root, "figures")

dir.create(output_root, recursive = TRUE, showWarnings = FALSE)
dir.create(table_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(figure_dir, recursive = TRUE, showWarnings = FALSE)

enc_long <- read.csv(file.path(base_dir, "subject_level_encoding_long.csv"))
tsc_long <- read.csv(file.path(base_dir, "subject_level_tsc_long.csv"))
network_summary <- read.csv(file.path(base_dir, "network_summary_master.csv"))
parcel_summary <- read.csv(file.path(base_dir, "parcel_summary_master.csv"))

enc_long <- enc_long %>%
  mutate(
    roi = factor(roi),
    condition = factor(condition, levels = c("raw", "srm"))
  )

tsc_long <- tsc_long %>%
  mutate(
    roi = factor(roi),
    condition = factor(condition, levels = c("anatomical", "shared"))
  )

write_xlsx_safe <- function(x, path, sheet_name = "Sheet1") {
  if (inherits(x, "list")) {
    write.xlsx(x, file = path, overwrite = TRUE)
  } else {
    write.xlsx(setNames(list(as.data.frame(x)), sheet_name), file = path, overwrite = TRUE)
  }
}

extract_fixed_effects_table <- function(model) {
  anova_tbl <- as.data.frame(anova(model))
  anova_tbl <- tibble::rownames_to_column(anova_tbl, var = "fixed_effect")
  names(anova_tbl) <- gsub("\\.", "_", names(anova_tbl))
  anova_tbl
}

add_sig_stars <- function(p) {
  case_when(
    is.na(p) ~ "",
    p < 0.001 ~ "***",
    p < 0.01 ~ "**",
    p < 0.05 ~ "*",
    TRUE ~ ""
  )
}

fmt5 <- function(x) {
  ifelse(is.na(x), NA_character_, sprintf("%.5f", x))
}

format_p5 <- function(p) {
  ifelse(
    is.na(p), NA,
    ifelse(p < 0.00001, "<0.00001", sprintf("%.5f", p))
  )
}

format_p_with_stars <- function(p) {
  case_when(
    is.na(p) ~ "",
    p < 0.00001 ~ "<0.00001***",
    p < 0.001 ~ paste0(sprintf("%.5f", p), "***"),
    p < 0.01 ~ paste0(sprintf("%.5f", p), "**"),
    p < 0.05 ~ paste0(sprintf("%.5f", p), "*"),
    TRUE ~ sprintf("%.5f", p)
  )
}

format_numeric_table <- function(df, cols = NULL) {
  out <- as.data.frame(df)
  if (is.null(cols)) {
    cols <- names(out)[vapply(out, is.numeric, logical(1))]
  }
  for (col in cols) {
    if (col %in% names(out)) {
      out[[col]] <- fmt5(out[[col]])
    }
  }
  out
}
```

# Overview

This document performs formal follow-up inference for the UBSN ROI project.

Main goals:

1. Test **within-network** improvement from raw to SRM-reconstructed encoding.
2. Test **within-network** improvement from anatomical to shared-space SRM TSC.
3. Fit **mixed-effects models** across all networks with subject as a repeated factor.
4. Export publication-ready fixed-effects tables, paired-test tables, and emmeans/post hoc tables.

# 1. Descriptive Network Summary

```{r descriptive-network-summary}
network_overview <- network_summary %>%
  select(
    roi,
    n_selected_parcels,
    n_voxels,
    srm_shared_mean_tsc,
    raw_group_mean_r,
    srm_group_mean_r,
    encoding_subject_delta_mean_r,
    subjects_improved,
    pct_improved
  ) %>%
  arrange(desc(srm_shared_mean_tsc))

network_overview

write_xlsx_safe(
  network_overview,
  file.path(table_dir, "network_overview_summary.xlsx"),
  sheet_name = "network_overview"
)
```

# 2. Within-Network Paired Tests

## 2.1 Encoding: Raw vs SRM

```{r paired-tests-encoding}
paired_encoding <- enc_long %>%
  select(roi, subject_index, condition, mean_r) %>%
  pivot_wider(names_from = condition, values_from = mean_r) %>%
  group_by(roi) %>%
  summarise(
    t_test = list(t.test(srm, raw, paired = TRUE)),
    mean_raw = mean(raw),
    mean_srm = mean(srm),
    mean_delta = mean(srm - raw),
    sd_delta = sd(srm - raw),
    cohens_d_paired = mean(srm - raw) / sd(srm - raw),
    .groups = "drop"
  ) %>%
  mutate(
    t_stat = map_dbl(t_test, ~ unname(.x$statistic)),
    df = map_dbl(t_test, ~ unname(.x$parameter)),
    p_value = map_dbl(t_test, ~ .x$p.value),
    conf_low = map_dbl(t_test, ~ .x$conf.int[1]),
    conf_high = map_dbl(t_test, ~ .x$conf.int[2]),
    p_fdr = p.adjust(p_value, method = "fdr"),
    significance = add_sig_stars(p_fdr)
  ) %>%
  select(
    roi, mean_raw, mean_srm, mean_delta, sd_delta, cohens_d_paired,
    t_stat, df, p_value, p_fdr, conf_low, conf_high, significance
  ) %>%
  arrange(desc(mean_delta))

paired_encoding_display <- format_numeric_table(paired_encoding)
paired_encoding_display

write_xlsx_safe(
  paired_encoding_display,
  file.path(table_dir, "paired_tests_encoding_raw_vs_srm.xlsx"),
  sheet_name = "paired_encoding"
)
```

## 2.2 SRM TSC: Anatomical vs Shared

```{r paired-tests-tsc}
paired_tsc <- tsc_long %>%
  select(roi, subject_index, condition, accuracy) %>%
  pivot_wider(names_from = condition, values_from = accuracy) %>%
  group_by(roi) %>%
  summarise(
    t_test = list(t.test(shared, anatomical, paired = TRUE)),
    mean_anatomical = mean(anatomical),
    mean_shared = mean(shared),
    mean_delta = mean(shared - anatomical),
    sd_delta = sd(shared - anatomical),
    cohens_d_paired = mean(shared - anatomical) / sd(shared - anatomical),
    .groups = "drop"
  ) %>%
  mutate(
    t_stat = map_dbl(t_test, ~ unname(.x$statistic)),
    df = map_dbl(t_test, ~ unname(.x$parameter)),
    p_value = map_dbl(t_test, ~ .x$p.value),
    conf_low = map_dbl(t_test, ~ .x$conf.int[1]),
    conf_high = map_dbl(t_test, ~ .x$conf.int[2]),
    p_fdr = p.adjust(p_value, method = "fdr"),
    significance = add_sig_stars(p_fdr)
  ) %>%
  select(
    roi, mean_anatomical, mean_shared, mean_delta, sd_delta, cohens_d_paired,
    t_stat, df, p_value, p_fdr, conf_low, conf_high, significance
  ) %>%
  arrange(desc(mean_delta))

paired_tsc_display <- format_numeric_table(paired_tsc)
paired_tsc_display

write_xlsx_safe(
  paired_tsc_display,
  file.path(table_dir, "paired_tests_tsc_anatomical_vs_shared.xlsx"),
  sheet_name = "paired_tsc"
)
```

# 3. Mixed-Effects Models

## 3.1 Encoding Model

```{r mixed-encoding}
enc_model_df <- enc_long %>%
  rename(
    `LLM encoding` = condition,
    Network = roi
  ) %>%
  mutate(
    `LLM encoding` = factor(
      `LLM encoding`,
      levels = c("raw", "srm"),
      labels = c("Raw + LLM", "SRM + LLM")
    ),
    Network = factor(Network)
  )

model_encoding <- lmer(
  mean_r ~ `LLM encoding` * Network + (1 | subject_index),
  data = enc_model_df
)

encoding_fixed_effects <- extract_fixed_effects_table(model_encoding) %>%
  rename(
    effect = fixed_effect,
    numDF = NumDF,
    denDF = DenDF,
    F_value = `F value`,
    p_value = `Pr(>F)`
  ) %>%
  mutate(
    effect = case_when(
      effect %in% c("`LLM encoding`", "LLM encoding") ~ "Raw + LLM vs SRM + LLM",
      effect == "Network" ~ "Network",
      effect %in% c("`LLM encoding`:Network", "LLM encoding:Network") ~ "(Raw + LLM vs SRM + LLM) x Network",
      TRUE ~ effect
    ),
    significance = add_sig_stars(p_value),
    p_value_print = format_p5(p_value)
  )

encoding_fixed_effects_display <- format_numeric_table(encoding_fixed_effects)
encoding_fixed_effects_display

write_xlsx_safe(
  list(
    fixed_effects = encoding_fixed_effects_display,
    model_coefficients = format_numeric_table(broom.mixed::tidy(model_encoding, effects = "fixed")),
    random_effects = format_numeric_table(broom.mixed::tidy(model_encoding, effects = "ran_pars"))
  ),
  file.path(table_dir, "mixed_model_encoding_results.xlsx")
)
```

## 3.2 SRM TSC Model

```{r mixed-tsc}
tsc_model_df <- tsc_long %>%
  rename(
    `Alignment method` = condition,
    Network = roi
  ) %>%
  mutate(
    `Alignment method` = factor(
      `Alignment method`,
      levels = c("anatomical", "shared"),
      labels = c("Anatomical alignment", "SRM shared space")
    ),
    Network = factor(Network)
  )

model_tsc <- lmer(
  accuracy ~ `Alignment method` * Network + (1 | subject_index),
  data = tsc_model_df
)

tsc_fixed_effects <- extract_fixed_effects_table(model_tsc) %>%
  rename(
    effect = fixed_effect,
    numDF = NumDF,
    denDF = DenDF,
    F_value = `F value`,
    p_value = `Pr(>F)`
  ) %>%
  mutate(
    effect = case_when(
      effect %in% c("`Alignment method`", "Alignment method") ~ "Anatomical alignment vs SRM shared space",
      effect == "Network" ~ "Network",
      effect %in% c("`Alignment method`:Network", "Alignment method:Network") ~ "(Anatomical alignment vs SRM shared space) x Network",
      TRUE ~ effect
    ),
    significance = add_sig_stars(p_value),
    p_value_print = format_p5(p_value)
  )

tsc_fixed_effects_display <- format_numeric_table(tsc_fixed_effects)
tsc_fixed_effects_display

write_xlsx_safe(
  list(
    fixed_effects = tsc_fixed_effects_display,
    model_coefficients = format_numeric_table(broom.mixed::tidy(model_tsc, effects = "fixed")),
    random_effects = format_numeric_table(broom.mixed::tidy(model_tsc, effects = "ran_pars"))
  ),
  file.path(table_dir, "mixed_model_tsc_results.xlsx")
)
```

# 4. EMMEANS and Post Hoc Tables

## 4.1 Encoding EMMEANS

```{r emmeans-encoding}

emmeans_encoding <- emmeans(model_encoding, ~ `LLM encoding` | Network)

emmeans_encoding_summary <- summary(emmeans_encoding) %>%
  as.data.frame() %>%
  mutate(
    df = suppressWarnings(as.numeric(df)),
    p_value_print = if ("p.value" %in% names(.)) format_p5(p.value) else NA
  )

emmeans_encoding_pairs <- pairs(emmeans_encoding, adjust = "fdr") %>%
  summary() %>%
  as.data.frame() %>%
  mutate(
    df = suppressWarnings(as.numeric(df)),
    p_value_print = if ("p.value" %in% names(.)) format_p5(p.value) else NA
  )

emmeans_encoding_summary_display <- format_numeric_table(emmeans_encoding_summary)
emmeans_encoding_pairs_display <- format_numeric_table(emmeans_encoding_pairs)

emmeans_encoding_summary_display
emmeans_encoding_pairs_display

write_xlsx_safe(
  list(
    emmeans = emmeans_encoding_summary_display,
    pairwise_contrasts = emmeans_encoding_pairs_display
  ),
  file.path(table_dir, "emmeans_encoding_results.xlsx")
)
```

## 4.2 TSC EMMEANS

```{r emmeans-tsc}
emmeans_tsc <- emmeans(model_tsc, ~ `Alignment method` | Network)

emmeans_tsc_summary <- summary(emmeans_tsc) %>%
  as.data.frame() %>%
  mutate(
    df = suppressWarnings(as.numeric(df)),
    p_value_print = if ("p.value" %in% names(.)) format_p5(p.value) else NA
  )

emmeans_tsc_pairs <- pairs(emmeans_tsc, adjust = "fdr") %>%
  summary() %>%
  as.data.frame() %>%
  mutate(
    df = suppressWarnings(as.numeric(df)),
    p_value_print = if ("p.value" %in% names(.)) format_p5(p.value) else NA
  )

emmeans_tsc_summary_display <- format_numeric_table(emmeans_tsc_summary)
emmeans_tsc_pairs_display <- format_numeric_table(emmeans_tsc_pairs)

emmeans_tsc_summary_display
emmeans_tsc_pairs_display

write_xlsx_safe(
  list(
    emmeans = emmeans_tsc_summary_display,
    pairwise_contrasts = emmeans_tsc_pairs_display
  ),
  file.path(table_dir, "emmeans_tsc_results.xlsx")
)
```

# 5. Publication-Style Tables

## 5.1 Type III ANOVA Tables

```{r publication-type3-tables}
encoding_type3_table <- encoding_fixed_effects %>%
  mutate(
    Factor = effect,
    `Sum Sq` = if ("Sum Sq" %in% names(.)) round(`Sum Sq`, 3) else NA_real_,
    NumDF = round(numDF, 3),
    DenDF = round(denDF, 3),
    `F-value` = round(F_value, 3),
    `p-value` = format_p_with_stars(p_value)
  ) %>%
  select(
    Factor,
    `Sum Sq`,
    NumDF,
    DenDF,
    `F-value`,
    `p-value`
  )

tsc_type3_table <- tsc_fixed_effects %>%
  mutate(
    Factor = effect,
    `Sum Sq` = if ("Sum Sq" %in% names(.)) round(`Sum Sq`, 3) else NA_real_,
    NumDF = round(numDF, 3),
    DenDF = round(denDF, 3),
    `F-value` = round(F_value, 3),
    `p-value` = format_p_with_stars(p_value)
  ) %>%
  select(
    Factor,
    `Sum Sq`,
    NumDF,
    DenDF,
    `F-value`,
    `p-value`
  )

encoding_type3_table
tsc_type3_table

write_xlsx_safe(
  list(
    encoding_type3_anova = encoding_type3_table,
    tsc_type3_anova = tsc_type3_table
  ),
  file.path(table_dir, "tables_type3_anova.xlsx")
)
```

## 5.2 EMMEANS Post Hoc Tables

```{r publication-emmeans-posthoc}

encoding_posthoc_table <- emmeans_encoding_pairs %>%
  mutate(
    Network = Network,
    Contrast = contrast,
    Estimate = round(estimate, 5),
    SE = round(SE, 5),
    df = round(df, 3),
    `t.ratio` = round(t.ratio, 3),
    `p-value` = format_p_with_stars(p.value)
  ) %>%
  mutate(
    SRM_plus_LLM_minus_Raw_plus_LLM = case_when(
      Contrast %in% c("Raw + LLM - SRM + LLM", "(Raw + LLM) - (SRM + LLM)") ~ round(-estimate, 5),
      Contrast %in% c("SRM + LLM - Raw + LLM", "(SRM + LLM) - (Raw + LLM)") ~ round(estimate, 5),
      TRUE ~ NA_real_
    ),
    Direction = case_when(
      p.value < 0.05 & SRM_plus_LLM_minus_Raw_plus_LLM > 0 ~ "SRM + LLM > Raw + LLM",
      p.value < 0.05 & SRM_plus_LLM_minus_Raw_plus_LLM < 0 ~ "Raw + LLM > SRM + LLM",
      TRUE ~ "No significant difference"
    )
  ) %>%
  select(
    Network,
    Contrast,
    Estimate,
    SRM_plus_LLM_minus_Raw_plus_LLM,
    SE,
    df,
    `t.ratio`,
    `p-value`,
    Direction
  )

tsc_posthoc_table <- emmeans_tsc_pairs %>%
  mutate(
    Network = Network,
    Contrast = contrast,
    Estimate = round(estimate, 5),
    SE = round(SE, 5),
    df = round(df, 3),
    `t.ratio` = round(t.ratio, 3),
    `p-value` = format_p_with_stars(p.value)
  ) %>%
  mutate(
    SRM_shared_space_minus_Anatomical_alignment = case_when(
      Contrast == "Anatomical alignment - SRM shared space" ~ round(-estimate, 5),
      Contrast == "SRM shared space - Anatomical alignment" ~ round(estimate, 5),
      TRUE ~ NA_real_
    ),
    Direction = case_when(
      p.value < 0.05 & SRM_shared_space_minus_Anatomical_alignment > 0 ~ 
        "SRM shared space > Anatomical alignment",
      p.value < 0.05 & SRM_shared_space_minus_Anatomical_alignment < 0 ~ 
        "Anatomical alignment > SRM shared space",
      TRUE ~ "No significant difference"
    )
  ) %>%
  select(
    Network,
    Contrast,
    Estimate,
    SRM_shared_space_minus_Anatomical_alignment,
    SE,
    df,
    `t.ratio`,
    `p-value`,
    Direction
  )

encoding_posthoc_table
tsc_posthoc_table

write_xlsx_safe(
  list(
    encoding_posthoc = encoding_posthoc_table,
    tsc_posthoc = tsc_posthoc_table
  ),
  file.path(table_dir, "tables_emmeans_posthoc.xlsx")
)
```

# 6. Cross-Network Association Tests

```{r cross-network-correlation}
cor_tsc_vs_srm_encoding <- cor.test(
  network_summary$srm_shared_mean_tsc,
  network_summary$srm_group_mean_r,
  method = "pearson"
)

cor_tsc_vs_encoding_delta <- cor.test(
  network_summary$srm_shared_mean_tsc,
  network_summary$encoding_subject_delta_mean_r,
  method = "pearson"
)

cor_raw_vs_srm_encoding <- cor.test(
  network_summary$raw_group_mean_r,
  network_summary$srm_group_mean_r,
  method = "pearson"
)

correlation_table <- tibble(
  comparison = c(
    "SRM shared TSC vs SRM+LLM encoding",
    "SRM shared TSC vs subject-level encoding delta",
    "Raw LLM encoding vs SRM+LLM encoding"
  ),
  estimate = c(
    unname(cor_tsc_vs_srm_encoding$estimate),
    unname(cor_tsc_vs_encoding_delta$estimate),
    unname(cor_raw_vs_srm_encoding$estimate)
  ),
  p_value = c(
    cor_tsc_vs_srm_encoding$p.value,
    cor_tsc_vs_encoding_delta$p.value,
    cor_raw_vs_srm_encoding$p.value
  ),
  conf_low = c(
    cor_tsc_vs_srm_encoding$conf.int[1],
    cor_tsc_vs_encoding_delta$conf.int[1],
    cor_raw_vs_srm_encoding$conf.int[1]
  ),
  conf_high = c(
    cor_tsc_vs_srm_encoding$conf.int[2],
    cor_tsc_vs_encoding_delta$conf.int[2],
    cor_raw_vs_srm_encoding$conf.int[2]
  )
) %>%
  mutate(significance = add_sig_stars(p_value))

correlation_table_display <- format_numeric_table(correlation_table)
correlation_table_display

write_xlsx_safe(
  correlation_table_display,
  file.path(table_dir, "cross_network_correlations.xlsx"),
  sheet_name = "correlations"
)
```

# 7. Statistical Figures

## 6.1 Network-level Encoding Improvement

```{r fig-encoding-delta, fig.width=11, fig.height=7}
fig_encoding_delta_df <- paired_encoding %>%
  arrange(desc(mean_delta)) %>%
  mutate(roi = factor(roi, levels = rev(roi)))

p_encoding_delta <- ggplot(fig_encoding_delta_df, aes(x = mean_delta, y = roi)) +
  geom_col(fill = "#E07A5F") +
  geom_errorbarh(aes(xmin = conf_low, xmax = conf_high), height = 0.18, color = "black") +
  labs(
    title = "Subject-level Paired Encoding Improvement by Network (SRM - Raw)",
    x = "Mean subject-level paired delta r (SRM + LLM - Raw + LLM)",
    y = NULL
  ) +
  theme(plot.title = element_text(face = "bold"))

p_encoding_delta

ggsave(
  filename = file.path(figure_dir, "network_encoding_improvement_barplot.png"),
  plot = p_encoding_delta,
  width = 11,
  height = 7,
  dpi = 300
)
```

## 6.2 Network-level SRM TSC Improvement

```{r fig-tsc-delta, fig.width=11, fig.height=7}
fig_tsc_delta_df <- paired_tsc %>%
  arrange(desc(mean_delta)) %>%
  mutate(roi = factor(roi, levels = rev(roi)))

p_tsc_delta <- ggplot(fig_tsc_delta_df, aes(x = mean_delta, y = roi)) +
  geom_col(fill = "#3D5A80") +
  geom_errorbarh(aes(xmin = conf_low, xmax = conf_high), height = 0.18, color = "black") +
  labs(
  title = "Subject-level Paired SRM Alignment Improvement by Network",
  x = "Mean subject-level paired delta accuracy (SRM shared space - anatomical alignment)",
  y = NULL
) +
  theme(plot.title = element_text(face = "bold"))

p_tsc_delta

ggsave(
  filename = file.path(figure_dir, "network_tsc_improvement_barplot.png"),
  plot = p_tsc_delta,
  width = 11,
  height = 7,
  dpi = 300
)
```

## 6.3 Subject-level Raw vs SRM Encoding by Network

```{r fig-encoding-box, fig.width=14, fig.height=8}
fig_encoding_box_df <- enc_long %>%
  mutate(
    `LLM encoding` = factor(
      condition,
      levels = c("raw", "srm"),
      labels = c("Raw + LLM", "SRM + LLM")
    )
  )

p_encoding_box <- ggplot(fig_encoding_box_df, aes(x = `LLM encoding`, y = mean_r, fill = `LLM encoding`)) +
  geom_boxplot(width = 0.65, outlier.shape = NA, alpha = 0.75) +
  geom_jitter(width = 0.08, alpha = 0.25, size = 0.9) +
  facet_wrap(~ roi, scales = "free_y") +
  scale_fill_manual(values = c("Raw + LLM" = "#8DA0CB", "SRM + LLM" = "#FC8D62")) +
  labs(
    title = "Subject-level Encoding Performance Across Networks",
    x = NULL,
    y = "Mean encoding r"
  ) +
  theme(
    legend.position = "top",
    strip.text = element_text(size = 9)
  )

p_encoding_box

ggsave(
  filename = file.path(figure_dir, "subject_level_encoding_boxplots.png"),
  plot = p_encoding_box,
  width = 14,
  height = 8,
  dpi = 300
)
```

## 6.4 Subject-level TSC by Network

```{r fig-tsc-box, fig.width=14, fig.height=8}
fig_tsc_box_df <- tsc_long %>%
  mutate(
    `Alignment method` = factor(
      condition,
      levels = c("anatomical", "shared"),
      labels = c("Anatomical alignment", "SRM shared space")
    )
  )

p_tsc_box <- ggplot(fig_tsc_box_df, aes(x = `Alignment method`, y = accuracy, fill = `Alignment method`)) +
  geom_boxplot(width = 0.65, outlier.shape = NA, alpha = 0.75) +
  geom_jitter(width = 0.08, alpha = 0.25, size = 0.9) +
  facet_wrap(~ roi, scales = "free_y") +
  scale_fill_manual(values = c("Anatomical alignment" = "#A6CEE3", "SRM shared space" = "#1F78B4")) +
  labs(
    title = "Subject-level SRM TSC Performance Across Networks",
    x = NULL,
    y = "TSC accuracy"
  ) +
  theme(
    legend.position = "top",
    strip.text = element_text(size = 9)
  )

p_tsc_box

ggsave(
  filename = file.path(figure_dir, "subject_level_tsc_boxplots.png"),
  plot = p_tsc_box,
  width = 14,
  height = 8,
  dpi = 300
)
```

## 6.5 Cross-Network Scatterplots

```{r fig-cross-network, fig.width=14, fig.height=6}
library(patchwork)

p_cross_1 <- ggplot(
  network_summary,
  aes(x = srm_shared_mean_tsc, y = srm_group_mean_r, color = roi)
) +
  geom_point(size = 3.3) +
  geom_smooth(method = "lm", se = FALSE, color = "grey35", linewidth = 0.8) +
  labs(
    title = "SRM TSC Accuracy vs SRM + LLM Encoding",
    x = "Shared-space TSC accuracy",
    y = "SRM + LLM group mean encoding r",
    color = "Network"
  ) +
  theme(legend.position = "bottom")

p_cross_2 <- ggplot(
  network_summary,
  aes(x = raw_group_mean_r, y = srm_group_mean_r, color = roi)
) +
  geom_point(size = 3.3) +
  geom_smooth(method = "lm", se = FALSE, color = "grey35", linewidth = 0.8) +
  labs(
    title = "Raw LLM Encoding vs SRM + LLM Encoding",
    x = "Raw group mean encoding r",
    y = "SRM + LLM group mean encoding r",
    color = "Network"
  ) +
  theme(legend.position = "bottom")

p_cross <- p_cross_1 + p_cross_2 +
  plot_layout(guides = "collect") +
  plot_annotation(theme = theme(legend.position = "bottom"))

p_cross

ggsave(
  filename = file.path(figure_dir, "cross_network_scatterplots.png"),
  plot = p_cross,
  width = 14,
  height = 6,
  dpi = 300
)
```

# 8. Optional Parcel-Level Descriptive Follow-up

```{r parcel-followup}
parcel_top20_srm <- parcel_summary %>%
  arrange(desc(srm_group_mean_r)) %>%
  select(roi, parcel_id, parcel_name, voxel_count, srm_group_mean_r) %>%
  head(20)

parcel_top20_raw <- parcel_summary %>%
  arrange(desc(raw_group_mean_r)) %>%
  select(roi, parcel_id, parcel_name, voxel_count, raw_group_mean_r) %>%
  head(20)

parcel_top20_delta <- parcel_summary %>%
  arrange(desc(delta_group_mean_r)) %>%
  select(roi, parcel_id, parcel_name, voxel_count, delta_group_mean_r) %>%
  head(20)

write_xlsx_safe(
  list(
    top20_srm_encoding = parcel_top20_srm,
    top20_raw_encoding = parcel_top20_raw,
    top20_delta_encoding = parcel_top20_delta
  ),
  file.path(table_dir, "parcel_top20_followup_tables.xlsx")
)

parcel_top20_srm
parcel_top20_raw
parcel_top20_delta
```

